---
title: "IAT"
output: html_notebook
---

##IAT
##Built-in error penalty procedure (preferred) Each trial’s latency is recorded to occurrence of the trial’s correct response; trials on which errors preceded the correct responses are included
##IAT only 3,4,6,7 block，区分联合任务为A相容,B;不相容;e.g. 3=A1,4=A2
  -   ① Designate combined tasks as A (for which faster performance will produce a positive score) and B (for which faster performance will produce a negative score). With counterbalancing, half of subjects will encounter A in Blocks 3 & 4, half in Blocks 6 & 7
  -   ②Discard all trials in Blocks 1, 2, and 5
  -   ③Identify blocks for combined task A as A1 and A2; those for combined task B as B1 and B2. If task A is Blocks 3 & 4, Block 3 is A1, Block 4 is A2
# ④Eliminate from remaining data (Blocks 3, 4, 6, and 7) only trials with latencies > 10,000 ms
# ⑤Eliminate all subjects for whom more than 10% of remaining trials have latencies faster than 300 ms
# ⑥Compute latency means (MnA1, MnA2, MnB1, MnB2) and SDs (SDA1, SDA2, SDB1, SDB2) for each of the four blocks for all remaining trials
# ⑦Compute two mean latency differences: B1–A1 = (MnB1 – MnA1) and B2–A2 = (MnB2 – MnA2)
# ⑧Compute an inclusive (not pooled) SD1 using all latencies in Blocks A1 & B1; another (SD2) using all latencies for A2 & B2 (SD2). These can be computed from means and SDs from Step 6 as shown in the lines below this table

# ⑨(B1-A1)/SD1,(B2-A2)/SD2
# ⑩D =  [(B1-A1)/SD1+(B2-A2)/SD2]/2

绝对值：0.2 = 小效应，0.5 = 中等效应，0.8 = 大效应


```{r IAT数据处理}

##数据预处理，区分相容与不相容的block，
IAT_data <- IAT_all%>%
  mutate(ID = as.character(ID)) %>%
  mutate(ParticipantID = as.character(ParticipantID)) %>%
  mutate(rt=as.numeric(rt))%>%
  group_by(ID) %>%
  mutate(
    version_attrib = case_when(
      task_id == "ability"~ (version_attrib[response == "0"& !is.na(version_attrib)]),
      TRUE ~ version_attrib),
    version_target = case_when(
      task_id == "ability"~ (version_target[response == "0"& !is.na(version_target)]),
      TRUE ~ version_target),
    version_attrib2 = case_when(
      task_id == "moral"~ (version_attrib2[response == "0"& !is.na(version_attrib2)]),
      TRUE ~ version_attrib2),
    version_target2 = case_when(
      task_id == "moral"~ (version_target2[response == "0"& !is.na(version_target2)]),
      TRUE ~ version_target2))%>%
  mutate(version = NA)%>%
  mutate(
    version = case_when(
    version_attrib == version_target & task_id == "ability" & screen_id == 3 ~ "A1",#相容为A，不相容为B，练习阶段为1，正式为2
    version_attrib == version_target & task_id == "ability" & screen_id == 4 ~ "A2",
    version_attrib == version_target & task_id == "ability" & screen_id == 6 ~ "B1",
    version_attrib == version_target & task_id == "ability" & screen_id == 7 ~ "B2",
    
    version_attrib != version_target & task_id == "ability" & screen_id == 3 ~ "B1",
    version_attrib != version_target & task_id == "ability" & screen_id == 4 ~ "B2",
    version_attrib != version_target & task_id == "ability" & screen_id == 6 ~ "A1",
    version_attrib != version_target & task_id == "ability" & screen_id == 7 ~ "A2",
    
    version_attrib2 == version_target2 & task_id == "moral" & screen_id == 3 ~ "A1",
    version_attrib2 == version_target2 & task_id == "moral" & screen_id == 4 ~ "A2",
    version_attrib2 == version_target2 & task_id == "moral" & screen_id == 6 ~ "B1",
    version_attrib2 == version_target2 & task_id == "moral" & screen_id == 7 ~ "B2",
    
    version_attrib2 != version_target2 & task_id == "moral" & screen_id == 3 ~ "B1",
    version_attrib2 != version_target2 & task_id == "moral" & screen_id == 4 ~ "B2",
    version_attrib2 != version_target2 & task_id == "moral" & screen_id == 6 ~ "A1",
    version_attrib2 != version_target2 & task_id == "moral" & screen_id == 7 ~ "A2",
      TRUE ~ version  # 如果没有满足条件的情况，保持原值
    )) %>%
    filter(screen_id %in% c(3, 4, 6, 7)) %>%
  filter(rt<=10000)%>%
   mutate(
    block_type = case_when(
      version %in% c("A1", "A2") ~ "compatible",
      version %in% c("B1", "B2") ~ "incompatible",))%>%
  mutate(con = case_when(
    block_type == "compatible" & condition %in% c("other", "negative") ~ "消极_朋友",
    block_type == "compatible" & condition %in% c("self", "positive") ~ "积极_自我",
    block_type == "incompatible" & condition %in% c("other", "positive") ~ "积极_朋友",
    block_type == "incompatible" & condition %in% c("self", "negative") ~ "消极_自我"
  ))

####计算出原始数据的均值，标准差
  IAT_data1<-IAT_data%>%
    group_by(ID,task_id,block_type,version) %>%  ##condition是4类标签的，task_id是moral和ability，version是A1,A2,B1,B2
  summarize(
    mean_rt = mean(rt),
    sd_rt = sd(rt),
    row_n = n(),
    se_rt = sd(rt) / sqrt(row_n))
print(IAT_data1)

##将错误的试次的反应时替换为平均反应时+600 ms
IAT_data<-IAT_data%>%
  left_join(IAT_data1%>%select(ID,task_id,block_type,version,mean_rt),by=c("ID","task_id","block_type","version"))%>%
  mutate(rt=ifelse(correct=="false",mean_rt+600,rt))

###计算取代完错误试次后的数据的均值，标准差
 IAT_data1<-IAT_data%>%
    group_by(ID,task_id,block_type,version) %>%  ##condition是4类标签的，task_id是moral和ability，version是A1,A2,B1,B2
  summarize(
    mean_rt = mean(rt),
    sd_rt = sd(rt),
    row_n = n(),
    se_rt = sd(rt) / sqrt(row_n))

```

```{r 描述性统计}

pacman::p_load("ggsignif")
#library(gghalves)
IAT_plot<-function(data){
  IAT_data<-data%>%
    ungroup()%>%
  mutate(task_id= case_when(
    task_id == "ability" ~ "能力",
    task_id == "moral"~ "道德",
  ))%>%
    group_by(ID,con,task_id)%>%
    summarize(
    mean_rt = mean(rt),
    sd_rt = sd(rt))%>%
    
  MANOVA(.,
       subID="ID",
       dv="mean_rt",
       within=c("task_id","con"),
       file = "IAT_con.doc")%>%#condition是4类标签的，task_id是moral和ability，block_type是匹配，不匹配
  EMMEANS("task_id", by="con")%>%
    
 EMMEANS("con", by="task_id")
  
  print(IAT_data)
  
 p_moral <- data %>%
  filter(task_id == "moral") %>%
  group_by(ID, con ) %>%
  summarize(
    RT = mean(rt),
    sd_rt = sd(rt),
    n = n() ,
     .groups = 'drop'
  )%>%
   mutate(
  RT = as.numeric(RT),
  con = factor(con, levels = c("积极_自我", "积极_朋友", "消极_自我", "消极_朋友"))
    )

print(p_moral)


p_ability <- data %>%
  filter(task_id == "ability") %>%
  group_by(ID, con ) %>%
  summarize(
    RT = mean(rt),
    sd_rt = sd(rt),
    n = n()  ,
    .groups = 'drop' 
  )%>%
   mutate(
  RT = as.numeric(RT),
 con = factor(con, levels = c("积极_自我", "积极_朋友", "消极_自我", "消极_朋友"))
   )

print(p_ability)
# 道德领域的数据绘图
p_moral_plot <- ggplot(p_moral, aes(x = con, y = RT, fill = con)) +
  geom_half_violin(side = "right", position = position_nudge(x = 0.2), trim = FALSE, alpha = 0.75) +
  geom_boxplot(width = 0.1, outlier.shape = NA, position = position_nudge(x = 0.2), color = "black", alpha = 0.75) +
  geom_jitter(aes(color = con), position = position_jitter(width = 0.1), size = 0.2, alpha = 0.75) +
  scale_y_continuous(limits = c(400, 1000), breaks = seq(500, 1000, by = 100)) +
  labs(title = "道德领域的反应时", x = "条件", y = "反应时") +
  theme_minimal()

# 能力领域的数据绘图
p_ability_plot <- ggplot(p_ability, aes(x = con, y = RT, fill = con)) +
  geom_half_violin(side = "right", position = position_nudge(x = 0.2), trim = FALSE, alpha = 0.75) +
  geom_boxplot(width = 0.1, outlier.shape = NA, position = position_nudge(x = 0.2), color = "black", alpha = 0.75) +
  geom_jitter(aes(color = con), position = position_jitter(width = 0.1), size = 0.2, alpha = 0.75) +
  scale_y_continuous(limits = c(400, 1000), breaks = seq(500, 1000, by = 100)) +
  labs(title = "能力领域的反应时", x = "条件", y = "反应时") +
  theme_minimal()

# 将图表排列成两行
plot <- ggarrange(p_moral_plot, p_ability_plot, ncol = 1, nrow = 2)
print(plot)
}
IAT_plot(IAT_data)

```

# IAT block_type(compatible,incompatible)*task_id(moral,	ability)
```{r IAT block_type(compatible,incompatible)*task_id(moral,	ability)}
IAT_RT_plot <- function(data,data_al,dat) {

#方差分析结果
  
IAT_ANOVA <-data%>% 
  mutate(task_id= case_when(
    task_id == "ability" ~ "能力",
    task_id == "moral"~ "道德",
  ))%>%
     mutate(block_type= case_when(
    block_type == "compatible" ~ "匹配",
    block_type == "incompatible" ~ "不匹配",
  ))%>%
    
  MANOVA(.,
       subID="ID",
       dv="mean_rt",
       within=c("task_id","block_type"),
       file = "IAT_com.doc")%>%#condition是4类标签的，task_id是moral和ability，block_type是匹配，不匹配
 EMMEANS("task_id", by="block_type") %>%
  EMMEANS("block_type", by="task_id")


 IAT_dat<-IAT_data%>%
    group_by(task_id,block_type) %>%  ##condition是4类标签的，task_id是moral和ability，version是A1,A2,B1,B2
  summarize(
    mean_rt = mean(rt),
    sd_rt = sd(rt),
    row_n = n(),
    se_rt = sd(rt) / sqrt(row_n))
 print(IAT_dat)
 
  IAT_data_al<-IAT_data%>%
    group_by(ID,block_type,version) %>%  ##condition是4类标签的，task_id是moral和ability，version是A1,A2,B1,B2
  summarize(
    mean_rt = mean(rt),
    sd_rt = sd(rt),
    row_n = n(),
    se_rt = sd(rt) / sqrt(row_n))%>%
  mutate(task_id="all")%>%
  bind_rows(IAT_data1,.)%>%#将两个子领域的D与总的D合并
  arrange(ID)
  print(IAT_data_al)
  # 创建rt的雨云图
  rt_plot1 <- ggplot(IAT_data_al ,aes(x=block_type,y=mean_rt, fill =block_type, colour =block_type))+
  geom_flat_violin(position = position_nudge(x = .25, y = 0),adjust =2, trim = FALSE)+
  geom_point(position = position_jitter(width = .15), size = .25)+
  geom_boxplot(aes(x =block_type, y =mean_rt),outlier.shape = NA, alpha = 0.3, width = .1, colour = "BLACK") +
ylab('rt')+xlab('condition')+coord_flip()+theme_cowplot()+guides(fill = FALSE, colour = FALSE) +
    facet_wrap(~task_id)+
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  ggtitle(" RT of IAT in different domains")
  
  print(IAT_ANOVA)
  print(rt_plot1)
  
 IAT_plot_rt <- IAT_dat%>%
 ungroup()%>%
   group_by(task_id,block_type)%>%
  ggplot(., aes(x = task_id, y = mean_rt, fill = block_type)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = mean_rt - se_rt, ymax = mean_rt + se_rt), position = position_dodge(width = 0.8), width = 0.25)+
  geom_text(
    aes(label = round(mean_rt,digits=3)),  # Add labels rounded to the nearest integer
    position = position_dodge(width = 0.8),
    vjust = -0.8,  # Adjust vertical position of labels
    size = 3  # Adjust label size if needed
  )+
  scale_fill_grey(start = 0.3) +
  scale_y_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50), expand = c(0, 0)) +
 guides(fill = guide_legend(title = "Condition"))+
  theme_minimal()  +
  labs(
    x = "domain",
    y = "RT",
    title = "RT of IAT in Different domains",
    caption = "Error bars indicate a standard error"
  )  +
  theme(
    plot.title = element_text(size = 20,
                              face = "bold",
                              margin = margin(b = 35)),
    
    axis.line = element_line(color = "#3D4852"),
    axis.ticks = element_line(color = "#3D4852"),
    panel.grid.major.y = element_line(color = "#DAE1E7"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank()
  )  
print(IAT_plot_rt)
}
IAT_RT_plot(IAT_data1,IAT_data)
```

#IAT的D值计算

```{r IAT的D值计算}
IAT_data_D2<-IAT_data1%>%
  ungroup()%>%
  select(-c("block_type","se_rt"))%>%
  pivot_wider(names_from = version, values_from = c(mean_rt, sd_rt,row_n)) %>%
  group_by(ID,task_id) %>% #task_id是领域(moral,ability)   #ID,version
  reframe(
    diff_B1A1 = round((mean_rt_B1 - mean_rt_A1), digits = 3),
    diff_B2A2 =round(( mean_rt_B2 - mean_rt_A2), digits = 3),
    SD_B1A1 = round((sqrt((((row_n_A1-1)*(sd_rt_A1^2)+(row_n_B1-1)*(sd_rt_B1^2))+((row_n_A1+row_n_B1)*((mean_rt_A1-mean_rt_B1)^2)/4))/(row_n_A1+row_n_B1-1))), digits = 3),
    SD_B2A2 = round((sqrt((((row_n_A2-1)*(sd_rt_A2^2)+(row_n_B2-1)*(sd_rt_B2^2))+((row_n_A2+row_n_B2)*((mean_rt_A2-mean_rt_B2)^2)/4))/(row_n_A2+row_n_B2-1))), digits = 3),
     D= round(((diff_B1A1/SD_B1A1) + (diff_B2A2/SD_B2A2))/2, digits = 3)
    )%>%
mutate(
    effect = case_when(
      abs(D) <= 0.2 ~ "small",
      abs(D) <= 0.5 ~ "mid",
      TRUE ~ "big")) #分为moral，ability两个领域的IAT_D
print(IAT_data_D)
IAT_data_D<-IAT_data_D%>%
  rename(domain=task_id,IAT_SE=D)
```
```{r}
IAT_data_D2%>%
  filter(task_id=="moral")%>%
TTEST(
  .,
  "D"
)

```
```{r}
IAT_data_D2%>%
  filter(task_id=="ability")%>%
TTEST(
  .,"D")

```
```{r}

IAT_D_plot <- function(data) {
  
  
  
  IAT_result <-data%>%
  mutate(task_id= case_when(
    task_id == "ability" ~ "能力",
    task_id == "moral"~ "道德",
 
  ))%>%
     ggplot(., aes(x = task_id, y = D, color = task_id))  +
    geom_boxplot(aes(color = task_id)) +
    geom_jitter(width = 0.2, alpha = 0.5, show.legend = FALSE) +
    labs(x = "领域", y = "D 值") +#, title = "IAT"
    theme_minimal()+
    theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(),
    # panel.background = element_rect(fill = "white")
  )
  print(IAT_result)
   ggsave("IAT_D.png", IAT_result, width = 10, height = 8, dpi = 300)
  IAT_summary <- data %>%
    group_by(task_id) %>%
    summarise(
      avg_D = mean(D, na.rm = TRUE),
      max_D = max(D, na.rm = TRUE),
      min_D = min(D, na.rm = TRUE),
      sd_D = sd(D, na.rm = TRUE),
      lower_95 = quantile(D, 0.025, na.rm = TRUE),
      upper_95 = quantile(D, 0.975, na.rm = TRUE)
    )
  print(IAT_summary)
  
  IAT_selected_data <- data %>%
    filter(task_id %in% c("moral", "ability"))%>%
    select(ID,task_id,D)%>%
  pivot_wider(names_from = task_id, values_from = D)
 print(IAT_selected_data)


 paired_t_test_result <- TTEST(IAT_selected_data, y=c("moral", "ability"), paired=TRUE,file="IAT_D.doc")
  
 print(paired_t_test_result)
  
}

IAT_D_plot(IAT_data_D2 )

```

```{r}
IAT_D_plot <- function(data) {
  
  
  
  IAT_result <-data%>%
  mutate(domain= case_when(
    domain == "ability" ~ "能力",
    domain == "moral"~ "道德",
 
  ))%>%
     ggplot(., aes(x = domain, y = IAT_SE, color = domain))  +
    geom_boxplot(aes(color = domain)) +
    geom_jitter(width = 0.2, alpha = 0.5, show.legend = FALSE) +
    labs(x = "领域", y = "D 值") +#, title = "IAT"
    theme_minimal()+
    theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.line = element_line(),
    # panel.background = element_rect(fill = "white")
  )
  print(IAT_result)
   ggsave("IAT_D.png", IAT_result, width = 10, height = 8, dpi = 300)
  IAT_summary <- data %>%
    group_by(domain) %>%
    summarise(
      avg_D = mean(IAT_SE, na.rm = TRUE),
      max_D = max(IAT_SE, na.rm = TRUE),
      min_D = min(IAT_SE, na.rm = TRUE),
      sd_D = sd(IAT_SE, na.rm = TRUE),
      lower_95 = quantile(IAT_SE, 0.025, na.rm = TRUE),
      upper_95 = quantile(IAT_SE, 0.975, na.rm = TRUE)
    )
  print(IAT_summary)
  
  IAT_selected_data <- data %>%
    filter(domain %in% c("moral", "ability"))%>%
    select(ID,domain,IAT_SE)%>%
  pivot_wider(names_from = domain, values_from = IAT_SE)
 print(IAT_selected_data)

 paired_t_test_result <- TTEST(IAT_selected_data, y=c("moral", "ability"), paired=TRUE,file="IAT_D.doc")
  
 print(paired_t_test_result)
 
 IAT_selected_data2 <- data %>%
    filter(domain %in% c("moral"))%>%
    select(ID,IAT_SE)
TTEST(IAT_selected_data2, "IAT_SE",file = "IAT_M.doc")
IAT_selected_data2 <- data %>%
    filter(domain %in% c("ability"))%>%
    select(ID,IAT_SE)
 TTEST(IAT_selected_data2, "IAT_SE",file = "IAT_A.doc")
  
}

IAT_D_plot(IAT_data_D)
```

